Logsums

### 2020-04-22 04_accessibility.Rmd
Repo cleanup
This includes a number of edits to the data elements related to switching the unit of analysis from tracts to block groups
Use 5000 meter threshold and remove blockgroups with no land

# tigris not working, manual download
#bg_poly <- tigris::block_groups("New York", county =  c("081", "047", "061", "005", "085"))
bg_poly <- st_read("/Users/gregmacfarlane/Library/Caches/tigris/tl_2019_36_bg.shp") %>%
  filter(GEOID %in% blockgroups$GEOID) %>%
  transmute(geoid = GEOID) %>%
  st_transform(32618)
```

@@

read_all_files <- function(pattern = pattern, path = "./"){
  map_df(list.files(path = path, pattern = pattern, full.names = TRUE), read_csv,
         col_types = list(geoid = col_character(), park_id = col_character()))
}
distances <- read_all_files(".csv", "data/nyc_shortest_paths_3500m/") %>%
  # filter out infinite paths
  filter(!is.infinite(distance)) %>%
  # add ten meters to all paths
  mutate(distance = distance + 10)
```

@@

bg_access <- bg_poly %>%
  left_join(logsums, by = "geoid")
```

>>>>

# tigris not working, manual download
#bg_poly <- tigris::block_groups("New York", county =  c("081", "047", "061", "005", "085"))
bg_poly <- st_read("/Users/gregmacfarlane/Library/Caches/tigris/tl_2019_36_bg.shp") %>%
  transmute(geoid = GEOID, p_water = AWATER / (AWATER + ALAND)) %>%
  filter(p_water < 1) %>%
  filter(geoid %in% blockgroups$GEOID) %>%
  st_transform(32618)
```

@@

read_all_files <- function(pattern = pattern, path = "./"){
  map_df(list.files(path = path, pattern = pattern, full.names = TRUE), read_csv,
         col_types = list(geoid = col_character(), park_id = col_character()))
}
distances <- read_all_files(".csv", "data/nyc_shortest_paths_5000m/") %>%
  # filter out infinite paths
  filter(!is.infinite(distance)) %>%
  # add ten meters to all paths
  mutate(distance = distance + 10)
```

@@

bg_access <- bg_poly %>%
  left_join(logsums, by = "geoid") %>%
  write_rds("data/bg_access.rds")
```
